\chapter{Application Evaluation, Outlook \& Future Work}\label{ch:outlook}

\section{Extensions}

\subsection*{Historic Images}

Some features from Bae et. al's work have been simplified away, so that
currently, no really historic photograph can be used. The app should therefore
be extended with another view controller presented after first and second frames
have been taken, in order for the user to label correspondences. These
correspondences can be used to fit a homography between the two views and warp
one of them accordingly.

\subsection*{Real-time User Guidance}

A higher rate of processing could be achieved by also using fast feature
tracking between robust pose estimations where the AKAZE detector is run. Bae et
al. use Lucas-Kanade-Tomasi tracking for this \citep{lucas1981,tomasi1991}, an
OpenCV implementation is already available. During automatic capture, it can be
observed that the found features often change abruptly between successive
frames. This and the fact that the number of found features changes strongly
results in the scale estimation jumping rapidly. A feature tracking may increase
the stability as the already-found points are found again, instead of radically
different ones.

\subsection*{Rephoto Postprocessing}

It is probable that despite all assistance, the user will not manage to
perfectly line up the original photograph with the current camera picture.  In
order to better register the original and final images, the latter can be warped
according to the last pose difference estimate. Bae et. al use an infinite
homography during the homing process, but the same method can be used after the
final capture. The infinite homography is the one between two views induced by
the plane at infinity, i.e.  the set of all projective points $(x,y,z,0)$ and
maps vanishing points in one view onto vanishing points in the other. Details
can be found in \citep[ch. 13.4]{h&z2004}.  Given the calibration matrices of
both views and their relative rotation, the homography can be computed and one
image can be warped with it by remapping the pixels.

\subsection*{Other Visualisation Options}\label{subsec:alternative_visualisation}

\citet{bae2010} explored different ways of guiding the user.  A side-by-side
view or a linear blend with the original photo were less helpful than the arrow
visualisation, but one could imagine offering different kinds, such as a
three-dimensional arrow which shows both parts of the necessary translation. A
more sophisticated idea is to project an approximation of the correct location
into the camera picture, but this would require a more detailed reconstruction
of the scene.

\subsection*{Online Platform}

It is envisioned to create an online community where
rephotographs can be uploaded by users.  There are web applications dedicated to
rephotography already, for example \emph{Third View}, a project directed by Mark
Klett dealing mostly with repeated captures of geographical landmarks, not
man-made structures \citep{thirdview}. However, it is a documentation project
and not community-driven. In contrast, the aforementioned Timera app also comes
with a community where users can upload their rephotos which are then presented
in the same fashion as in the app itself, or old photos for others to use as a
reference.

A platform letting users upload their pictures is also the subject of another
thesis by \citet{weber2015}. The web service developed in this work sports the
following features.

\begin{itemize}
   \item Users can upload, rate and comment on rephotographs.
   \item Rephotos can be viewed in detail in an overlay and a slider masks the
      images just as in the iOS app presented here.
    \item Rephotos can be tagged with metadata, including time, location or
       title.
    \item Rephotos can be filtered by timespan between the two images, the
       geographic location and the category.
    \item A map displays the locations for which users have shared their
       rephotos.
    \item The two images can be registered in the web form via identification of
       corresponding points. With OpenCV, a homography is estimated to better
       register the images.
\end{itemize}

The web service supplies an application programming interface of which the mobile
app should make use in the future. Rudimentary provisions have been made, but
the authentication must be implemented and the HTTP request adapted to interface
with the server.

\section{Usability \& Performance}

The focus of this work was the theoretical exploration and evaluation of Bae et.
al's approach to computational rephotography, not on the design of release-ready
application. As such, some functionality is missing and the app is not
extensively tested. Notable shortcomings are
\begin{enumerate}
   \item In the gallery inside the app, the final captures of each rephoto are
      shown as thumbnails. Should multiple rephotos be based on the same
      original, they will be indistinguishable. The thumbnails should be made
      more meaningful.

   \item Deletion of rephotos works via the user's gallery, where the rephoto
      album created by the app is visible. Deletion will leave invalid entries
      in the database which should be cleaned up by the app. More reasonably
      perhaps, deletion should be offered inside the app.

      % \item Since rephotos are saved as tuples of URLs it may happen that the user
      %    takes multiple rephotos with the same original. Currently, both will be
      %    displayed in the gallery inside the app, but the \code{MainViewController}
      %    picks the first record for which the URL of the selected image matches so
      %    that only the first rephoto can be reviewed. Additional logic would

   \item The upload of rephotos is experimentally hard-coded to work with a test
      server and is a blocking request.

   \item To enhance user experience, a choice between different overlays should
      be offered, where at this time only an edge overlay is implemented. The
      edge overlay could also be made more helpful by post-processing it into a
      more distinctive subset of lines to remove noisy clutter when fine-grained
      patterns are present (e.g. vegetation).

   \item All frames are matched with the first frame so it would suffice to
      compute the keypoints once for it and reuse them. Currently, the keypoints
      are recomputed for every relative pose estimation.

   \item The application requires iOS 8, but actually has few dependencies on
      it. The user interface employs \code{UIVisualEfffectView}s which were
      previously unavailable. It should be fairly straightforward to create
      versions of the UI without these elements.

   \item The calibration data cannot currently be loaded from a user-supplied
      file. Ideally, since not all devices will have the exact same camera
      characteristics, each user would have to individually calibrate their
      camera.

   \item The rephotography makes use of the simple
      \code{UIImagePickerController} which is presented modally. This makes the
      flow of the app less seamless. For instance, when the
      \code{PhotoChooserController} is presented and the user loads a reference image,
      the image picker will pop up, but upon image selection, one is not
      immediately shown the camera, but is briefly shown the photo chooser again
      before the rephoto starts with yet another \code{UIImagePickerController}
      (this time in camera mode instead of gallery).
      Furthermore, the possibility to modify the camera stream is limited to
      affine transformations, which precludes projective transformation. This
      would be necessary to implement the image warping used by \citet{bae2010}.
      Also, images are captured by a timer, it would be more intuitive to
      attempt to process frames as they come and simply drop them if no CPU time
      is available which would also scale more easily to other devices. Both
      could be accomplished by rebasing the app on the much more customisable
      \code{AVFoundation} framework which gives more low-level access to the device's
      camera at the cost of significantly more development effort.
      For this, OpenCV wrappers exist already which would simplify processing the frames.  

   \item The application has only been tested on a single device. While it
      should work on iPhones as well, this could not be tested and some tuning
      may be necessary.

   \item The application creates a photo album for the rephotos with the name
      \emph{Rephoto-Album}, without checking if it already exists.

   \item Every finished rephotograph is saved. There should be an option to
      discard an attempt in the result view.

\end{enumerate}


