\chapter{Appendix A --- Bugs}

Some bugs in the SDK have been discovered in the making of the software.
\begin{enumerate}

   \item When using \code{UIImagePickerController} in camera mode with disabled
      camera controls---necessary to provide custom controls---zooming and then
      rotating the device will create a black bar at one side of the image.
      Rotating back will remove it but hide the otherwise visible zoom level
      indicator. It is necessary to implement a manual zooming and apply an
      appropriate transform to the camera stream.

   \item When all images from the app-created rephoto album are deleted, the
      album will not be shown in the gallery anymore, but \code{ALAssetsLibrary}
      does not permit adding images to it or recreate an album of the same name.
      Since developers are encouraged to move to the more recent Photos
      framework, this problem is not likely to get fixed. The bug ID is
      20992021 (unacknowledged by Apple).

   \item It is not feasible to support background and foreground transitions
      while using a timed capture on \code{UIImagePickerController} as has been
      done here. If the app becomes inactive while an image is being captured,
      it appears as if sometimes the data is released and therefore unavailable when
      transitioning back to the foreground. This results in an exception being
      thrown, which the developer can do nothing about, except avoid
      \code{UIImagePickerController} for timed capture. The bug ID is 19953748
      (unacknowledged by Apple).
\end{enumerate}
